Vragenlijst thesis evaluatie

### 2015-06-30 doc/template/conclusion.tex
alles opslagen
versie voor mama
conclusie

\chapter{Conclusion}
\label{cha:conclusion}
The final chapter contains the overall conclusion. It also contains
suggestions for future work and industrial applications.

>>>>

\chapter{Conclusion}
\label{chapter5:conclusion}

This paper presents an adaption to the basic FlipIt game by \citep{FlipIt} to model an attacker with a delay.  We have

The work presented in this paper represents an initial caclulation of the strategies. 
\subsection{Further work}

\begin{description}
\item Analysing other renewal strategies.
\item Delay for the defender. It takes some time to make a patch if a new exploit is found.
\item The delay a variable that can change with every Flip.
\item ..
\end{description}
